The \dealii Library, Version 9.7

### 2025-08-20 9.7/paper.tex
Help with wrapping lines and pages.

    via \texttt{TensorProductMatrixCreator::create\_1d\_ghost\_penalty\_matrix}. For Cartesian cells, the local penalty matrix can be constructed by exploiting the tensor-product structure   

@@

    of degrees of freedom across adjacent cells via \texttt{FETools::cell\_to\_face\_patch}.

@@

features and bugfixes --

@@

\begin{figure}[hb]
\includegraphics{taskflow-vs-tbb/plots-figure1.pdf}\hfill
\includegraphics{taskflow-vs-tbb/plots-figure2.pdf}
\caption{Assembly times in a modified step-32 (left: temperature
  matrix assembly, right: temperature right-hand side assembly)
  comparing TBB and Taskflow with and without coloring. These figures
  correspond to the middle row of \cite[Fig. 4]{TKB16}. Lines with
  squares match ``Implementation 2'' in \cite{TKB16}; the lines with
  circles labeled ``colored'' match ``Implementation 3'' therein.}
\label{fig:tbb-vs-taskflow}
\end{figure}

>>>>

    via \texttt{TensorProductMatrixCreator::create\_1d\_ghost\_penalty\_matrix()}. For Cartesian cells, the local penalty matrix can be constructed by exploiting the tensor-product structure   

@@

    of degrees of freedom across adjacent cells via the
    \texttt{FETools::cell\_to\_face\_patch()} function.

@@

new features and bugfixes --

@@

\begin{figure}[tb]
\includegraphics{taskflow-vs-tbb/plots-figure1.pdf}\hfill
\includegraphics{taskflow-vs-tbb/plots-figure2.pdf}
\caption{Assembly times in a modified step-32 (left: temperature
  matrix assembly, right: temperature right-hand side assembly)
  comparing TBB and Taskflow with and without coloring. These figures
  correspond to the middle row of \cite[Fig. 4]{TKB16}. Lines with
  squares match ``Implementation 2'' in \cite{TKB16}; the lines with
  circles labeled ``colored'' match ``Implementation 3'' therein.}
\label{fig:tbb-vs-taskflow}
\end{figure}
